Automated topic naming to support analysis of software maintenance activities

### 2010-08-21 icse/icse2011.tex
conclusions and future work editted

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (NFR) (quality requirements)~\cite{Cleland-Huang2006}. 
Their approach was similar to ours, as they mined keywords from their own NFR catalogues~\cite{chung99}.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They managed a recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our worked differed because we had a more comprehensive set of terms based on the taxonomy we chose.
We also wanted a common taxonomy that allows us to make cross-project comparison, which was not one of their objectives.
The objective of Cleland-Huang's study was to identify new NFRs for system development, yet our objective was to recover those latent NFRs from commit-log messages of the project. 
Another difference was that our data was far less structured that the requirements documents used in their study.
%There are several reasons we did not follow this route. 
%One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. 
%Secondly, we wanted to compare across projects. 
%Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. 
%A common taxonomy allows us to make cross-project comparison. 
%Although subject to the assumption that all projects conceive of these terms in the same way.
%Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the commit-log messages of the project.

In the same vein, Mockus and Votta~\cite{Mockus00} studied a large-scale industrial change-tracking system. 
They also leveraged WordNet, but only for word roots. 
They felt the synonyms would be non-specific and cause errors. 
A nice contribution was access to system developers, with whom they could validate their labels. 
Since we try to bridge different organizations, these interviews are infeasible (particularly in the distributed world of open-source software).

@@

% % Not sure we need this
% Mens et al.~\cite{mens08icsm} conducted an empirical study of Eclipse, a popular Java IDE, to verify the claims of Lehman~\cite{lehman97sms}.
% % They concerned themselves with source code only, and found Law Seven, ``Declining Quality'', to be too difficult to assess: ``[we lacked an] appropriate measurement of the evolving quality of the system as perceived by the users \cite[p. 388]{mens08icsm}''. 
% This paper examines the notions of quality in terms of a consistent ontology, as Mens
et al. call for in their conclusions.

@@

% XXX vanity or space.. 
% Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.

@@

% para 4 summarize and hammer contribution
% NE not a fan of this phrasing -> % In conclusion, 
Previous topic analysis research produced topics that needed to be manually labelled, but topics without labels are difficult to interpret.
To improve this, we leveraged software engineering standards to produce a method of domain specific topic labelling.
Since the word-list technique is not project specific, it can be used to compare multiple projects.
We demonstrated multiple supervised and unsupervised methods of topic labelling, including multi-label learners.
We provided a case study and visualization of NFR related topics in MaxDB 7.500 and MySQL 3.23. 
During the case study we manually labelled hundreds of topics by hand then used these annotations to validate the positive performance of topic labelling techniques.
The implication of our paper is that topics with labels are more useful than unlabelled topics. To furnish stakeholders with labelled topics, our technique provides many methods of automatic topic labelling.

%\subsection{Future Work}

 % para 5 future work
 % Future work
There are several avenues of further investigation.  
More external validation would be useful. 
Although we validated our comparisons using a mailing list for each project, interviews with developers would provide more detail. 
We also think multi-label learning techniques, although in their infancy, are crucial in understanding cross-cutting concerns such as NFRs. 
Finally, we would like to extend this analysis to other domains, to see what patterns might occur in, for example, an end-user facing software product.
 % Talk to people
% We want to investigate developer attitudes related to these labels: i.e., when we label a topic, was the developer expressing positive or negative qualities about that label?  
% It is difficult to map abstract qualities to particular messages. % what?
%  % This is disjointed and needs more context
% On question we seek to answer is if a ``quality'' discussion about more than just corrective maintenance? %In this study we take the position that any type of maintenance has to do with software quality.

>>>>

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (NFR) (quality requirements)~\cite{Cleland-Huang2006}. 
Their approach was similar to ours, as they mined keywords from their own NFR catalogues~\cite{chung99}.
%One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. 
They managed a recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. 
Instead, they developed a supervised classifier by using human experts to identify an NFR training set. 
Our worked differed because we had a more comprehensive set of terms based on the taxonomy we chose.
We also wanted a common taxonomy that allows us to make cross-project comparison; this was not one of their objectives.
The objective of Cleland-Huang's study was to identify new NFRs for system development, yet our objective was to recover those latent NFRs from commit-log messages of the project. 
Another difference was that our data was far less structured than the requirements documents used in their study.
%There are several reasons we did not follow this route. 
%One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. 
%Secondly, we wanted to compare across projects. 
%Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. 
%A common taxonomy allows us to make cross-project comparison. 
%Although subject to the assumption that all projects conceive of these terms in the same way.
%Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the commit-log messages of the project.

In the same vein, Mockus and Votta~\cite{Mockus00} studied a large-scale industrial change-tracking system. 
They also leveraged WordNet, but only for word roots as they felt the synonyms would be non-specific and cause errors. 
Mockus et al. had access to system developers, with whom they could validate their labels. 
Since we try to bridge different organizations, these kind of interviews are infeasible (particularly in the distributed world of open-source software).

@@

%XXXXXXXXXXXX OPTIONAL
% Not sure we need this
Mens et al.~\cite{mens08icsm} conducted an empirical study of Eclipse, a popular Java IDE, to verify the claims of Lehman~\cite{lehman97sms}.
% They concerned themselves with source code only, and found Law Seven, ``Declining Quality'', to be too difficult to assess: ``[we lacked an] appropriate measurement of the evolving quality of the system as perceived by the users \cite[p. 388]{mens08icsm}''. 
This paper examines the notions of quality in terms of a consistent ontology, as Mens
et al. call for in their conclusions.

@@

% XXX vanity or space.. 
%XXXXXXXXXXXX OPTIONAL
 Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.

@@

%XXXXXXXXXXXXXXXX I think we need to suggest a couple of uses.

% para 4 summarize and hammer contribution
% NE not a fan of this phrasing -> % In conclusion, 
Previous topic analysis research produced topics that needed to be manually labelled, but topics without labels are difficult to interpret.
To improve this, we leveraged software engineering standards to produce a method of domain specific topic labelling.
Since the word-list technique is not project specific, it can be used to compare multiple projects.
We demonstrated multiple supervised and unsupervised methods of topic labelling, including multi-label learners.
We provided a case study and visualization of NFR related topics in MaxDB 7.500 and MySQL 3.23. 
During the case study we manually labelled hundreds of topics by hand and then used these annotations to validate the positive performance of topic labelling techniques.
The implication of our paper is that topics with labels are more useful than unlabelled topics. To furnish stakeholders with labelled topics, our technique provides many methods of automatic topic labelling.

%XXXXXXXX Optional  
\subsection{Future Work}

 % para 5 future work
 % Future work
There are several avenues of further investigation.  
More external validation would be useful. 
Although we validated our comparisons using a mailing list for each project, interviews with developers would provide more detail. 
We also think multi-label learning techniques, although in their infancy, are crucial in understanding cross-cutting concerns such as NFRs. 
We also want to leverage different kinds of artifacts to discover threads of NFR-related discussions that occur between multiple kinds of artifacts.
Finally, we would like to extend this analysis to other domains, to see what patterns might occur in, for example, an end-user facing software product.
 % Talk to people
% We want to investigate developer attitudes related to these labels: i.e., when we label a topic, was the developer expressing positive or negative qualities about that label?  
% It is difficult to map abstract qualities to particular messages. % what?
%  % This is disjointed and needs more context
% On question we seek to answer is if a ``quality'' discussion about more than just corrective maintenance? %In this study we take the position that any type of maintenance has to do with software quality.
